### 2016-03-08 paper/algorithm.tex
yasu

\section{Swarm Fusion Method}

Swarm Fusion is a natural multi-core extension of Fusion Move
Method. Take a multi-threading environment to explain our idea, which is
also applicable to other parallel computation environments such as cloud
computing. Every thread $T_i$ keeps track of a solution $S_i$, and
repeats updating $S_i$ by fusion ($i = 1, 2, \cdots N$). Two parameters
$\alpha_i$ and $\beta_i$ control the behavior of fusion steps in each
thread $T_i$. $\alpha_i$ specifies how many solution proposals are to be
generated from proposal generation schemes. Similarly, $\beta_i$
specifies how many solutions in the other threads are to be
fused. Suppose $N=4$, $\alpha_1 = 2$, and $\beta_1 = 3$. In this
configuration, the first thread $T_1$ fuses its current solution $S_1$,
two new proposal solutions (e.g., by randomly picking two proposal
generation schemes), and the current solutions $(S_2, S_3, S_4)$ in the
other three threads. This is a multi-way fusion with a non-submodular
energy in general, and message passing algorithm such as
TRW~\cite{kolmogorov} can be used. Sequential QPBO application is
another.

Our model is flexible. For example, a parallel fusion move algorithm by
Lempitsky et al.~\cite{viktor} is a special case of ours, where $\alpha_$

>>>>

\section{Swarm Fusion Method}
\yasu{need to polish, reads very bad.}  Swarm Fusion is a natural
parallel extension of Fusion Move Method. Take a multi-threading
environment to explain our idea, which is also applicable to other
parallel computation environments such as cloud computing. Assume we
have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$. There are two places to
collect solutions or solution proposals for fusion. First, the {\it
proposal pool} can generate new solution proposals on request.
%
Second, the {\it solution pool} stores the solutions that have been
fused by the threads. At default, each thread keeps only a current
solution in the pool, but the scheme can be more general. Two
parameters $\alpha_i$ and $\beta_i$ control the behavior of each fusion
step in $T_i$. The thread collects $\alpha_i$ solution proposals
from the proposal pool and $\beta_i$ solutions from the solution pool
for fusion in each step.
%
Furthermore, one can also control how to choose proposal generation
schemes and/or solutions from the pools.

Our framework is general, and it is easy to verify that existing
parallel fusion algorithms are just our special cases.
%
For example, the parallel fusion algorithm by Lempitsky et
al.~\cite{viktor} always performs binary fusion between the current
solution and another label, which can be achieved by setting $\alpha_i =
1$ and $\beta_i = 0$ for all the threads. The algorithm by
Veksler~\cite{olga} or Dejong et al.~\cite{dejong} hierarchically fuses
solutions starting from solution proposals. The algorithm can be
realized by setting $\alpha_i = 1, \beta_i = 0$ initially, then use
$\alpha_i = 0, \beta_i=1$  for the rest of the algorithm.

standard models.

We now illustrate the power of Swarm Fusion framework for three problems
in Computer Vision.

Suppose $N=4$, $\alpha_1 = 2$, and $\beta_1 = 3$. In this
configuration, the first thread $T_1$ fuses its current solution $S_1$,
two new proposal solutions (e.g., by randomly picking two proposal
generation schemes), and the current solutions $(S_2, S_3, S_4)$ in the
other three threads. This is a multi-way fusion with a non-submodular
energy in general, and message passing algorithm such as
TRW~\cite{kolmogorov} can be used. Sequential QPBO application is
another.

Our model is flexible. For example, a parallel fusion move algorithm by
Lempitsky et al.~\cite{viktor} is a special case of ours, where $\alpha_i$
